Topic modeling on EU and the USA research projects

### 2017-06-15 thesis_report/draft_thesis.tex
minor fixes in Related work on the thesis report

Inspired by Griffiths and Steyvers, L.Sun and Y.Yin wrote a paper, "Discovering
themes and trends in transportation research using topic modeling",
\cite{Sun201749} about topic modeling in transportation research. 
Considering approximately 17000 abstracts of articles published on 22 
leading journals in transportation research as documents, they infer 50 
topics by using LDA. Compared to "Finding scientific topics", Sun and 
Yin use more than one journal (22 popular journals) and they
investigate the journal-topic distribution and journal similarity. In our
analysis, we assume that EU and USA are 2 countries (like 2 different journals),
with different proportions of documents-projects, and we visualize the topic
similarity of the two countries per framework programme.

@@

Details about the implementation, system specs etc.

@@

>>>>

Inspired by Griffiths and Steyvers, L.Sun and Y.Yin wrote a paper, "Discovering
themes and trends in transportation research using topic modeling",
\cite{Sun201749} about topic modeling in transportation research. 
Considering approximately 17000 abstracts of articles published on 22 
leading journals in transportation research as documents, they infer 50 
topics by using LDA. Compared to "Finding scientific topics", Sun and 
Yin use more than one journal (22 popular journals) and they
investigate the journal-topic distribution and journal similarity. In our
analysis, we identify the EU and the USA as 2 regions (like 2 different journals),
with different proportions of documents-projects, and we visualize the topic
similarity of the two regions per framework programme.

@@

For the implementation, we used the Gensim package (Radim Řehůřek,
2009)\cite{rehurek_lrec} which implements an efficient online LDA algorithm, to
extract the topics of a given corpus. Gensim uses a fast implementation of
online LDA parameter estimation based on "Online Learning for Latent Dirichlet
Allocation".\cite{onlineLDAvb} The algorithm runs in constant memory, which
means that the size of the training corpus does not affect memory footprint, so
it can process corpus larger than RAM.

The LDA model requires some basic input parameters; for both datasets we chose
the number of topics $K=10$. The hyperparameter $\alpha$, which affects the
sparsity of the document-topic distribution $\theta$, is by default a symmetric
$\frac{1.0}{num_topics} = 0.1$ prior. We left the default value of $chunksize=2000$. We
started with 50 iterations and later we increased the number of iterations,
until the training converged. We used 7000 iterations for each framework
programme of the EU dataset and 8000 for each framework of the USA dataset. In
the USA dataset, we used $passes=1$, while in the EU dataset we switched to
$passes=2$, because the training could not converge, despite the large number of
the iterations.

The implementation was run on a computer with an Intel® Xeon® Processor E5-1410
(10MB Cache, 2.8 GHz, 4 cores, 8 threads) and RAM=12 GB.

@@

In this section, we show our main results. We focus on finding differents
between the two datasets in terms of topic distribution and later we 
investigate the evolution of the topics over time of each dataset separately.

\subsection{Discovering topics on EU and USA projects}

wordclouds per FP?

\subsection{Topic evolution over time}
